Simple connectome inference from partial correlation statistics in calcium imaging

### 2014-06-18 article.tex
update text on pca

Finally since there is a high correlation between neurons,
we filter some more noise through a principal component analysis. From the $|V|$
eigen vectors, we kept $80\%$ of the eigen vectors which have the largest eigen
value. In the context of the challenge, this assumption was deduced from ground
truth of provided networks.

@@

\item[GENIE3] (\cite{huynhthu2010inferring}) translates the inference of the
network of $p$ neurons into $p$ supervised learning tasks. For each task,
the fluorescence of a neuron is predicted from the fluorescence
of all other neurons using a tree based ensemble such as
random forest (\cite{breiman2001random}). The tree ensemble associate a
variable importance scores (\cite{louppe2013understanding})
to each neuron used in the predictions.

The following parameters are used
$10000$ trees, $\log_2{p}$ neurons are randomly selected at each tree
node to split the data and the maximal tree depth is constrained
to 1, 2 or 3.
\end{description}

>>>>

To filter more noise before computing the partial correlation, we kept
$80\%$ of the eigen vectors which have the largest eigen
value (\cite{tipping1999mixtures}). In the context of the challenge, this
assumption was deduced from ground truth of provided networks.

@@

\item[GENIE3] (\cite{huynhthu2010inferring}) translates the inference of the
network of $p$ neurons into $p$ supervised learning tasks. For each task,
the fluorescence of a neuron is predicted from the fluorescence
of all other neurons using a tree based ensemble such as
random forest (\cite{breiman2001random}). The tree ensemble associate a
variable importance scores (\cite{louppe2013understanding})
to each neuron used in the predictions, which is used as a connectivity
score. The following parameters are used
$10000$ trees, $\log_2{p}$ neurons are randomly selected at each tree
node to split the data and the maximal tree depth is constrained
to 1, 2 or 3.
\end{description}
